Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2016-12-09 Draft_1.tex
First Draft complete

        \Large
        Word Count - PLACEHOLDER\\
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

@@

\subsubsection{Neural Networks}
\label{sec:NeuralNetwork}

>>>>

        \Large
        Word Count - 3108\\
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

@@

\subsubsection{Neural Networks}
\label{sec:NeuralNetwork}
In recent years the use of Neural Networks, more specifically Deep Neural Networks, in the solving of computational problems has dramatically increased. More recently, this technique has been applied to the problem of natural language processing. As discussed in the \hyperref[sec:fNLP]{Natural Language Processing section}, it was shown that assigning varyng labels to words and phrases (i.e. categorisation) made up a large proportion of the processes, a job neural networks are wellsuited to, and often associated with \cite{NeuralNetworks}.

The first process requrired in the use of neural networks, is the conversion of raw text into a vector-base representation, giving a sentance as a set of vectors. The sentence is then passed into the neural network \cite{NeuralNetworks}. The network proposed by R.Collobert and J. Weston in 2008 contained multiple layers, each serving its own purpose \cite{NeuralNetworks}. Initially the network identifies word features, before using this data to calculate the probability of each synset of each word.

It was found by the authors that their model provided good results, though, in order to get these results, a large amount of time was deicated to training \cite{NeuralNetworks}.
